Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-06 Report/convergence_centralized.tex
updated after Nam's correction

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Objective function should be bounded below
\item[(b)] Feasible set should be compact
\item[(c)] Sequence of objective values should be strictly decreasing
\item[(d)] Uniqueness of the minimizer in each step.
\end{itemize}
\review{Note that condition (d) is required to ensure strict monotonicity of the objective sequence. Therefore, by using above conditions (a)-(c) along with \cite[Th. 3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}. Then, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by Algorithm \ref{algo-1} is a stationary point of nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}. The term iterates correspond to the stacked vector of solution variables obtained in each iteration.}

@@

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}
The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence with the gradient of \eqref{con-dc} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, using the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by following \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}

>>>>

\begin{comment}
The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Objective function should be bounded below
\item[(b)] Feasible set should be compact
\item[(c)] Sequence of objective values should be strictly decreasing
\item[(d)] Uniqueness of the minimizer in each step.
\end{itemize}
\review{Note that condition (d) is required to ensure strict monotonicity of the objective sequence. Therefore, by using above conditions (a)-(c) along with \cite[Th. 3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}. Then, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by Algorithm \ref{algo-1} is a stationary point of nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}. The term iterates correspond to the stacked vector of solution variables obtained in each iteration.}

@@

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}
The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence with the gradient of \eqref{con-dc} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, using the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by following \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}
\end{comment}

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Objective function should be bounded below
\item[(b)] Feasible set should be compact
\item[(c)] Sequence of objective values should be strictly decreasing
\item[(d)] Uniqueness of the minimizer in each step.
\end{itemize}
Note that condition (d) is required to ensure strict monotonicity of the objective sequence. Therefore, by using above conditions (a)-(c) along with \cite[Th. 3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}. Then, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by the Algorithm \ref{algo-1} is a stationary point of original nonconvex problem formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

Before discussing the convergence analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{RcL} \label{con} \neqsub
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& \hat{f}(\mx,\my,\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0 \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0 \eqsub \label{con-cvx}
\end{IEEEeqnarray}
where \me{g_2} and \me{\hat{f}} are convex, \me{h} is linear, and \me{g_0} and \me{g_1} are convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both variables. The constraint \eqref{con-dc} corresponds to either \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} represents to either  \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} correspondingly. Other convex constraints are handled by \eqref{con-cvx} and the feasible set of \eqref{con} is given by 
\iftoggle{single_column}{
\begin{equation}
\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{equation}
}{\begin{align}
\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
& \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{align}}

We use the following notations to discuss the convergence of Algorithm \ref{algo-1}. Since it involves two nested loops, \textit{i.e.}, one for \ac{SCA} and another for \ac{AO}, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}. Let \me{\mx}, \me{\my}, and \me{\mz} be the vector stacking all transmit precoders, receive beamformers, and other optimization variables used in \eqref{eqn-6} and \eqref{eqn-mse-1} respectively. Let us consider \ac{AO} step \eqn{i} with fixed \eqn{\my}. The solution obtained in the \eqn{\ith{k}} \ac{SCA} step is given by \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}. As \eqn{k \to \infty}, objective sequence converges, and the respective solution is denoted by \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}. Similarly, while alternating the optimization variables for fixed \eqn{\mx}, as \eqn{k \to \infty}, the solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}}. In the following, we show that the conditions listed in (a)-(d) are satisfied by Algorithm \ref{algo-1}.

To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures strong convexity of \eqn{f} in each step \cite{scutari-1}. Thus, due to strong convexity in \eqn{f}, uniqueness of the minimizer is ensured in each \ac{SCA} step \cite{yang_yang,scutari-1}.

\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} to exploit the uniqueness of the minimizer at each iteration. However, we note that upon convergence \eqn{f} is equal to \eqn{\hat{f}}. Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.

To begin with, let us consider the variable \me{\my} begin fixed for the \me{\ith{i}} \ac{AO} with the optimal value found in previous iteration \me{i-1} as \me{\iter{\my}{\lpoint}{i-1}}. In order to solve for \me{\mx} in \ac{SCA} iteration \me{k}, we linearize the nonconvex function \me{g_0} using previous \ac{SCA} iterate \me{\iter{\mx}{k}{i}} of \me{\mx} as
\hat{g}_o(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \triangleq {g}_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1}) + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
\hat{g}_o(\mx,\iter{\my}{\lpoint}{i-1};\iter{\mx}{k}{i}) \triangleq {g}_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1}) \\ + \nabla g_0(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1})^{\mathrm{T}} (\mx - \iter{\mx}{k}{i}).
\me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}} as the solution in the \me{\ith{k}} iteration. The point \me{\iter{\mx}{k+1}{i}} and \me{\iter{\mz}{k+1}{i}}, which minimize the objective function satisfy
Thus, the sequence \me{\{f(\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k}{i})\}} is nonincreasing. Using strong convexity of the objective, we can show that the inequalities in \eqref{con-convergence} are strict, \textit{i.e.}, the sequence of objectives returned by Algorithm \ref{algo-1} is strictly decreasing. To this end, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step. At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows
where \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}} and \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Therefore, by using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds strictly in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \to \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \to \infty}. Now, by utilizing the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. Since the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of objective sequence in each \ac{AO} step \eqn{{i}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon convergence of the sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}

Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}. Since the constraint \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, we have
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}
\reviewF{Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}. Moreover, note that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is also present in objective function \eqref{mod_obj}, therefore, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges. }

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm. In order to do that, let us use single index \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}. It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
Using global index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector staking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

Using the arguments in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges. Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}. However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded. Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th. 3.6]{rudin1964principles}.

We now show that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. To do this, let us consider a subsequence \eqn{\{\ma^{t_j} |j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}} is a limit point of \eqn{\{\ma^t\}}. Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, it follows from Appendices \ref{c-a} and \ref{mcity} that
\begin{equation} \label{seq_mon}
\dotsc < f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}) < \dotsc.
\end{equation}
Note that the inequality in \eqref{seq_mon} holds while alternating the optimization variables as shown in \eqref{fixed_point}. Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain
\begin{equation} \label{limpoint}
\lim_{t \to \infty} f(\ma^{t}) = \lim_{j \to \infty} f(\ma^{t_j}) = f(\lim_{j \to \infty} \ma^{t_{j}}) = f(\bar{\ma}).
\end{equation}

Let us prove the stationarity of \eqn{\bar{\ma}} by contradiction. Assume that \eqn{\bar{\ma}} is not a stationary point, then there exist some other point \eqn{\ma^\prime \in \{\ma^t\}}, such that \eqn{\nabla f (\bar{\ma})^\tran (\ma^\prime - \bar{\ma}) < 0} and \eqn{f(\bar{\ma}) > f(\ma^\prime)}. Since \eqn{\ma^\prime} is a point in \eqn{\{\ma^t\}}, there exist a subsequence that converges to \eqn{\ma^\prime}, for which \eqn{\ma^\prime} is a limit point. However, from \eqref{limpoint}, we have \eqn{f(\bar{\ma}) = f(\ma^\prime)} for all limit points of any convergent subsequence of \eqn{\{\ma^t\}}, which is a contradiction.

Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point.

Now to prove that \eqn{\bar{\ma}} is also a stationary point of original nonconvex problem \eqref{con}, we show the equivalence between gradients of subproblem \eqref{con-m} and \eqref{con} at stationary point \eqn{\bar{\ma}}. In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point for \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
\begin{equation} \label{kkt_expr}
\textstyle	\nabla \hat{f}(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla {g}_0(\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0
\end{equation}
for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\bar{\ma} \in \mc{F}}.

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}
The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence with the gradient of \eqref{con-dc} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
If follows immediately from \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr} that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by following \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can prove that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative method is a stationary point of problem \eqref{con}.}

### 2015-11-06 Report/convergence_distributed.tex
updated after Nam's correction

However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus, achieving improved speed of convergence. Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update. Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed. Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is not guaranteed in each update. Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure the convergence of the beamformer iterates.

>>>>

However, to avoid the nested iterations, the proposed method performs group update of all the variables at once to obtain the transmit and the receive beamformers with the limited number of iterations, thus, achieving improved speed of convergence. Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update. Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed. Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is also not guaranteed in each update. Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure the convergence of the beamformer iterates.

### 2015-11-06 Report/mse_formulation.tex
updated after Nam's correction

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receive beamformers. The optimization subproblem to find the transmit precoders for fixed receive beamformers \me{\mvec{w}{l,k,n}} is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
The optimal transmit precoders for fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively and by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.

In all simulations, the objective of Algorithm \ref{algo-1} converges. \reviewF{However, to discuss the theoretical convergence of subproblems \eqref{eqn-9}, \eqref{eqn-9--1} and \eqref{eqn-mse-2}, following modifications are considered. (i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective with quadratic term as in \eqref{mod_obj} to ensure strong convexity in objective function. (ii) To guarantee the boundedness of feasible sets, we trivially bound \eqn{\beta_{l,k,n}}'s and \eqn{\mvec{w}{l,k,n}}'s as \eqn{\beta_{l,k,n} \leq P_{\max}} and \eqn{\|\mvec{w}{l,k,n}\|^2 \leq 1} in subproblems \eqref{eqn-9} and \eqref{eqn-9--1}. However, these additional constraints on optimization variables has no impact on final solution or objective. Using this, convergence of Algorithm \ref{algo-1} is discussed in Appendix \ref{sec-3.5}.}

>>>>

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receivers. The optimization subproblem to find transmit precoders for fixed \me{\mvec{w}{l,k,n}} is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
The optimal transmit precoders for fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively and by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.

In all simulations, objective sequence generated by Algorithm \ref{algo-1} converges. \reviewF{However, for formal convergence analysis, following modifications are assumed. (i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective in \eqref{mod_obj}, which exhibits strong convexity. (ii) Moreover, for some large \eqn{B_{\max} \gg P_{\max}}, we limit \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq B_{\max}} without altering the solution, to ensure the feasible sets of \eqref{eqn-9} and \eqref{eqn-9--1} bounded. The additional constraint on \eqn{\beta_{l,k,n}} is necessary, since \eqref{eqn-6.3} need not be tight when \eqn{\gamma_{l,k,n} \to 0}. Due to this, \eqn{\beta_{l,k,n}} becomes unbounded, since any value of \eqn{\beta_{l,k,n}} satisfying \eqref{eqn-6.3} with inequality, satisfies \eqref{eqn-6.3} with equality. Finally, with these changes, convergence of Algorithm \ref{algo-1} is dealt in Appendix \ref{sec-3.5}.}
